# Seismic Hazard Assessment

```{r}
#| include: true
root <- normalizePath(here::here())
source(file.path(root,"scripts","setup","setup.R"))
source(file.path(root, "scripts", "setup", "report.R"))
```

## Probabilistic Seismic Hazard Assessment (PSHA)

{{< include /_chapters/psha.model.md >}}

{{< include /_chapters/psha.uncertainty.md >}}

{{< include /_chapters/psha.disagg.md >}}

### Hazard Curves and Spectra {#sec-hazard_results}

{{< include /_chapters/psha.aep.md >}}

{{< include /_chapters/psha.poe.md >}}

```{r}
#| echo: false
#| results: asis
for (i in seq_len(nrow(SiteTable))) {
  .knitReportBlock(
    path = "/_tbl/RMw.qmd",
    stem = "hazard-rmw-table",
    sites = SiteTable,
    i = i,
    vars = list(ID.target = ID.gmdp),
    root = root,
    context = "hazard RMw table"
  )
}
rm(i)
```

```{r}
#| echo: false
#| results: asis
if (nrow(SiteTable)) {
  NOTE <- .deckNote("sha", "Seismic Hazard Assessment", "The hazard curves and probabilistic spectra are developed in the %s annex.")
  if (nzchar(NOTE)) cat("\n\n", NOTE, "\n\n", sep = "")
  rm(NOTE)
}
```

## Seismic Source Characterization {#sec-ssc}

### Seismotectonic Setting

```{r}
#| echo: false
#| results: asis
NGR::knitBlock(
  path   = sprintf("/_chapters/ssm.tectonic.%s.md", params$ssm),
  stem   = sprintf("ssm-tectonic-%s", tolower(params$ssm)),
  labels = "keep",
  root   = root
)
```

### Seismicity

```{r}
#| echo: false
#| results: asis
NGR::knitBlock(
  path   = sprintf("/_chapters/ssm.seismicity.%s.md", params$ssm),
  stem   = sprintf("ssm-seismicity-%s", tolower(params$ssm)),
  labels = "keep",
  root   = root
)
```

### Neotectonics

```{r}
#| echo: false
#| results: asis
NGR::knitBlock(
  path   = sprintf("/_chapters/ssm.faults.%s.md", params$ssm),
  stem   = sprintf("ssm-faults-%s", tolower(params$ssm)),
  labels = "keep",
  root   = root
)
```

### Regional Sources (SSM) {#sec-ssm}

```{r}
#| echo: false
#| results: asis
if (is.null(params$ssm) || !nzchar(params$ssm)) {
  stop("params.yml: params$ssm must name the seismic source model chapter (_chapters/ssm.<ID>.md).", call. = FALSE)
}
NGR::knitBlock(
  path = sprintf("/_chapters/ssm.%s.md", params$ssm),
  stem = sprintf("ssm-%s", tolower(params$ssm)),
  labels = "keep",
  root = root
)
```

## Ground Motion Models (GMM) {#sec-gmm_appendix}

{{< include /_chapters/gmm.model.md >}}

{{< include /_chapters/gmm.trees.md >}}

{{< include /_chapters/gmm.uncertainty.md >}}

`r .deckNote("sha", "Seismic Hazard Assessment", "The seismic hazard assessment is documented in the %s annex.")`

## Deterministic Seismic Hazard Assessment (DSHA) {#sec-mce}

{{< include /_chapters/dsha.model.md >}}

{{< include /_chapters/dsha.uncertainty.md >}}

{{< include /_chapters/dsha.results.md >}}

```{r}
#| echo: false
#| results: asis
for (i in seq_len(nrow(SiteTable))) {
  .knitReportBlock(
    path = "/_tbl/Scenarios.qmd",
    stem = "dsha-scenarios",
    sites = SiteTable,
    i = i,
    vars = list(ID.target = ID.gmdp),
    root = root,
    context = "declared scenario parameters"
  )
  .knitReportBlock(
    path = "/_tbl/DSHA.qmd",
    stem = "dsha-table",
    sites = SiteTable,
    i = i,
    vars = list(ID.target = ID.gmdp, Vs30.target = 760),
    root = root,
    context = "DSHA comparison table"
  )
  .knitReportBlock(
    path = "/_tbl/Scenarios.PGA.qmd",
    stem = "dsha-scenarios-pga",
    sites = SiteTable,
    i = i,
    vars = list(ID.target = ID.gmdp),
    root = root,
    context = "scenario PGA by condition"
  )
}
rm(i)
```

```{r}
#| echo: false
#| results: asis
if (nrow(SiteTable)) {
  NOTE <- .deckNote("sha", "Seismic Hazard Assessment", "The deterministic scenario spectra and their comparison with the probabilistic demand are developed in the %s annex.")
  if (nzchar(NOTE)) cat("\n\n", NOTE, "\n\n", sep = "")
  rm(NOTE)
}
```

## Seismic Record Selection {#sec-srs}

{{< include /_chapters/srs.model.md >}}

```{r}
#| echo: false
#| results: asis
if (!is.null(SelectionTable)) {
  for (i in seq_len(nrow(SelectionTable))) {
    .knitSelectionBlock(
      path = "/_tbl/SRS.qmd",
      stem = "srs-records",
      selections = SelectionTable,
      i = i,
      root = root,
      context = "SRS chapter"
    )
  }
  NOTE <- .deckNote("srs", "Seismic Record Selection", "The selected records and their verifications are presented in the %s annex.")
  if (nzchar(NOTE)) cat("\n\n", NOTE, "\n\n", sep = "")
  rm(NOTE)
  rm(i)
}
rm(list = intersect(c("SiteTable", "SelectionTable"), ls()))
```

